\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-11-13 preliminaries.tex
updated preliminaties.tex

\subsection{Consistent Estimation}
The simplest estimator is simply to invert a quantile. Indeed,
fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
\[
B_i = \mathbf 1_{X_i>\theta_0}, 
\]
where $\mathbf 1_A$ is the indicator of the event $A$. We have
\[
P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
\]
so that 
\begin{equation}
\label{eq:estimator_naive}
{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
\end{equation}
is a consistent estimator for $\theta$ in the distributed setting of
Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
support of $f$. As the variance of $P_n$ is
$F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, a delta method
calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
asymptotically normal with variance
\begin{equation*}
  \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
\eta(\theta-\theta_0)}.
\end{equation*}
In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
ARE of ${\theta}_n$ is $\eta(\theta - \theta_0)\sigma^2$.

>>>>

\subsection{Consistent Estimation}
The simplest estimator is simply to invert a quantile. Indeed,
fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
\[
B_i = \mathbf 1_{X_i<\theta_0}, 
\]
where $\mathbf 1_A$ is the indicator of the event $A$. We have
\[
P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
\]
so that 
\begin{equation}
\label{eq:estimator_naive}
{\theta}_n = \theta_0 - F^{-1}\left( P_n \right)
\end{equation}
is a consistent estimator for $\theta$ in the distributed setting of
Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
support of $f$. As the variance of $P_n$ is
$F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)$, a delta method
calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
asymptotically normal with variance
\begin{equation*}
  \frac{F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)}{f^2(\theta_0-\theta)} = \frac{1}{
\eta(\theta_0-\theta)}.
\end{equation*}
In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
ARE of ${\theta}_n$ is $\eta(\theta_0 - \theta)\sigma^2$.
